---
title: "10_2021-42-set5"
author: "Timothée Bigot"
date: "07/10/2021"
output: html_document
---
############################################################################################################################
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r env_loading, include=FALSE}
# Load packages, data and functions
library(sctransform)
library(reticulate)
library(Seurat)
library(htmlwidgets)
library(DT)
library(plotly)
library(kableExtra)
library(monocle3)
library(DDRTree)
library(pheatmap)
library(reshape2)
library("gridExtra")
library(knitr)

# Path to the folder containing scripts used in the analysis
CWD <- "/media/station/DATA2/01_tim/01_these/01_etv6/02_scripts/" 
#  Path to the folder that will contain output objects
OUTPUT_PATH <- "/media/station/DATA2/01_tim/01_these/01_etv6/04_pseudotime_data/Objets_R_Demux/last_but_not_least/"

# Load the R scripts of "manual" functions
source(paste(CWD, "Mito_function.R", sep="/"))
source(paste(CWD, "CheckPackage.R", sep="/"))
source(paste(CWD, "as_cell_data_set.R", sep="/"))

# Set the random number seed
set.seed(1234)
```

```{r path1_loading, include=FALSE}
# Load path for files
PATH_HUMAN_DATA1 <- "/media/station/DATA2/01_tim/01_these/00_Fli1/00_data/00_sets_meso/05_2021-42-set5/01_cellranger_run2021-42-set5_GRCh382020A_CR5/outs/filtered_feature_bc_matrix/"
# SAMPLE1 <- "D6"
PATH_HTO_DATA1 <- "/media/station/DATA2/01_tim/01_these/00_Fli1/00_data/00_sets_meso/05_2021-42-set5/CIte-seq-Count/umi_count/"
```
## Data preprocessing
```{r Sample_loading, include=FALSE}
# Read 10X data
fli1_data <- Read10X(data.dir = PATH_HUMAN_DATA1, strip.suffix = T)

# Create the Seurat object and applies filters 
Not_processed_Seurat1 <- CreateSeuratObject(counts = fli1_data, min.cells = 3, min.features = 200)
```

```{r}
# Load in the UMI matrix
umi_sparse <- GetAssayData(object = Not_processed_Seurat1, slot = "counts")
# Setup Seurat object
hashtag1 <- CreateSeuratObject(counts = umi_sparse, assay = "RNA")
# Normalize RNA data with log normalization
hashtag1 <- NormalizeData(hashtag1, display.progress = T)
# Find and scale variable genes
hashtag1 <- FindVariableFeatures(hashtag1, do.plot = T, selection.method = "vst", nfeatures = 2000, display.progress = T)
hashtag1 <- ScaleData(hashtag1,genes.use = rownames(hashtag1)) #, vars.to.regress = c("S.Score", "G2M.Score") ,display.progress = FALSE)
```
#Import souporcell assignations
```{r}
all_clusters <- read.csv("/media/station/DATA2/01_tim/01_these/02_Souporcell/07_2021-42-set5/2021-42-set5/clusters.tsv", header = T, sep = "\t")

hashtag1@meta.data$souporcell_classif <- "NA"
hashtag1@meta.data[gsub(x = all_clusters[all_clusters$status == "doublet",]$barcode,"-1",""),]$souporcell_classif <- "doublet"
hashtag1@meta.data[gsub(x = all_clusters[all_clusters$status == "unassigned",]$barcode,"-1",""),]$souporcell_classif <- "unassigned"
hashtag1@meta.data[gsub(x = all_clusters[all_clusters$assignment == "0",]$barcode,"-1",""),]$souporcell_classif <- "cluster0"
hashtag1@meta.data[gsub(x = all_clusters[all_clusters$assignment == "1",]$barcode,"-1",""),]$souporcell_classif <- "cluster1"
hashtag1@meta.data[gsub(x = all_clusters[all_clusters$assignment == "2",]$barcode,"-1",""),]$souporcell_classif <- "cluster2"
# hashtag1@meta.data[gsub(x = all_clusters[all_clusters$assignment == "3",]$barcode,"-1",""),]$souporcell_classif <- "cluster3"
```
##Demultiplexing results
#Cells classification
Cells classification as singlets, doublets and negative/ambiguous cells for HTOdemux and doublet, negative and HTO for Multiseq
Overall, multiseq results seem  better than HTOdemux
- HTOdemux vs Clusterisation
```{r}
table(hashtag1@meta.data$souporcell_classif)
```
- MULTIseqDemux vs Clusterisation
```{r}
table(hashtag1@meta.data$MULTI_ID,hashtag1@meta.data$souporcell_classif)
```
### interroger barcodes en particulier pour IGV
```{r}
# CB identifié par IGV
all_clusters[all_clusters$barcode == c("TCTTTCCTCACATAGC-1"),]
```

```{r}
# CB identifié par IGV
all_clusters[all_clusters$barcode == c("TCAGGATGTACTTAGC-1"),]
```

### longueur et noms des Doublets
```{r}
rownames(hashtag1@meta.data[hashtag1@meta.data$souporcell_classif == "doublet",])
length(rownames(hashtag1@meta.data[hashtag1@meta.data$souporcell_classif == "doublet",]))
```

##### Exome vs SNPs
```{r}

```
#Scatterplot
```{r, message=FALSE}
FeatureScatter(hashtag1, feature1 = "F417.II.2", feature2 = "P214.III.8", group.by = "hash.ID")
```
#Violinplot (features)
```{r, message=FALSE}
VlnPlot(hashtag1,features = c("nFeature_RNA"),pt.size = 0.1, log = TRUE,  group.by = "hash.ID")
```
### Violin plots (HTO counts)
```{r, message=FALSE}
VlnPlot(hashtag1,features = c("nCount_HTO"),pt.size = 0.1, log = TRUE,  group.by = "hash.ID")
```
###UMAP based on HTO
```{r, message=FALSE}
DimPlot(hashtag1, group.by = "hash.ID")
```
###Ridge plots
**Visualize enrichment for selected HTOs with ridge plots**
```{r, fig.height = 4, message=FALSE}
RidgePlot(hashtag1, assay = "HTO", features = rownames(GetAssayData(hashtag1,assay = "HTO"))[1:2],ncol = 2, group.by = "HTO_maxID")
```
###Select cells
```{r cell_select1, results='asis'}
cluster0 <- row.names(subset(hashtag1@meta.data, souporcell_classif == "cluster0" ))
cluster1 <- row.names(subset(hashtag1@meta.data, souporcell_classif == "cluster1" ))
cluster2 <- row.names(subset(hashtag1@meta.data, souporcell_classif == "cluster2" ))
# cluster3 <- row.names(subset(hashtag1@meta.data, souporcell_classif == "cluster3" ))

Clusters_identified1 = c(cluster0,cluster1,cluster2)
clean.subset1 <- subset(x = hashtag1, cells = Clusters_identified1)
VlnPlot(clean.subset1,features = c("nFeature_RNA", "nCount_RNA"),pt.size = 0.1, log = TRUE,  group.by = "souporcell_classif")
```
###Create Seurat definitive object
```{r}
  #1- QC (fait à partir de la sous sélection)
  Seurat8 <- QC_function_mito_threshold(Seurat = clean.subset1, mito_threshold = 0.1, do_plot = TRUE)
```

```{r}
  #2- Find variable genes
  Seurat8 <- FindVariableFeatures(object = Seurat8, 
                            assay = "RNA", selection.method = "vst", nfeatures = 2000,
                            verbose = FALSE)
  Seurat8 <- ScaleData(Seurat8, 
                      assay="RNA",
                      verbose = FALSE,
                      features = rownames(Seurat8),
                      do.center = TRUE)
  Seurat8 <- RunPCA(object = Seurat8,
                   assay = "RNA",
                   verbose = FALSE,
                   features =  VariableFeatures(object = Seurat8),
                   seed.use = 1234,
                   npcs = 50)
  ElbowPlot(Seurat8, ndims = 50, reduction = "pca")
```
# Scorer les genes pour les composantes
```{r}
  Seurat8 <- ProjectDim(object = Seurat8,
                  nfeatures.print = 10,
                  dims.print = 1:16)
  Seurat8 <- RunTSNE(object = Seurat8,
                  do.fast = TRUE, 
                  seed.use = 1234,
                  dims = 1:16,
                  perplexity = 40)
  Seurat8 <- FindNeighbors(object = Seurat8, 
                  dims = 1:16, 
                  verbose = FALSE, 
                  force.recalc = TRUE, 
                  reduction = "pca",
                  k.param = 30)
  Seurat8 <- FindClusters(object = Seurat8, 
                  resolution = 0.5,
                  verbose = T,
                  random.seed = 1234)
  Seurat8 <- RunUMAP(object = Seurat8, reduction = "pca", seed.use = 1234, dims = 1:16)
save(Seurat8, file = paste0(OUTPUT_PATH, "10_2021-42-set5", ".Robj"))
```
###UMAPs
```{r tSNE_HTO_seurat_1}
ggplotly(DimPlot(Seurat8, reduction = "umap", label = F, pt.size = 1, ncol = 2, group.by = "souporcell_classif", split.by = "orig.ident"))
```
```{r}
ggplotly(DimPlot(Seurat8, reduction = "umap", group.by = "souporcell_classif", label = F, pt.size = 1, ncol = 2))
table(Seurat8@meta.data$souporcell_classif)
```
```{r tSNE_HTO_seurat_1}
DimPlot(Seurat1, reduction = "umap", label = F, pt.size = 1, ncol = 2, group.by = "RNA_snn_res.0.2", split.by = "orig.ident")
DimPlot(Seurat1, reduction = "umap", label = F, pt.size = 1, ncol = 2, group.by = "RNA_snn_res.0.2", split.by = "ETV6status")
```
# Identité des clusters possibles grâce à table(souporcell, HTO DEMUX ou MULTI ID), aux quelques mut dans BAM, PCR et Exome
```{r}
Seurat8@meta.data$identity <- "NA"
Idents(Seurat8) <- "souporcell_classif"
Seurat8@meta.data[Seurat8@meta.data$souporcell_classif == "cluster0",]$identity = "CtrlA"
Seurat8@meta.data[Seurat8@meta.data$souporcell_classif == "cluster2",]$identity = "CtrlB"
Seurat8@meta.data[Seurat8@meta.data$souporcell_classif == "cluster1",]$identity = "R337Q.II.1"
# Seurat8@meta.data[Seurat8@meta.data$souporcell_classif == "cluster3",]$identity = "j6F417.II.2"
ggplotly(DimPlot(Seurat8, pt.size = 1, ncol = 2, reduction = "umap", group.by = "identity"))
```
```{r}
table(Seurat8@meta.data$identity,Seurat8@meta.data$souporcell_classif)
```
# ETV6status
```{r}
Seurat8@meta.data$ETV6status <- "NA"
Idents(Seurat8) <- "identity"
Seurat8@meta.data[Seurat8@meta.data$identity == "CtrlA",]$ETV6status = "01_Témoins"
Seurat8@meta.data[Seurat8@meta.data$identity == "CtrlB",]$ETV6status = "01_Témoins"
Seurat8@meta.data[Seurat8@meta.data$identity == "R337Q.II.1",]$ETV6status = "02_Patient"
# Seurat8@meta.data[Seurat8@meta.data$identity == "j6P214.III.8",]$ETV6status = "02_Patients"
ggplotly(DimPlot(Seurat8, pt.size = 1, ncol = 2, reduction = "umap", group.by = "ETV6status"))
```
```{r}
table(Seurat8@meta.data$ETV6status,Seurat8@meta.data$souporcell_classif)
```

# orig.ident
```{r}
Seurat8@meta.data$orig.ident <- "NA"
Seurat8@meta.data[rownames(Seurat8@meta.data),]$orig.ident = "01_J5"
ggplotly(DimPlot(Seurat8, pt.size = 1, ncol = 2, reduction = "umap", group.by = "orig.ident"))
```
```{r}
table(Seurat8@meta.data$orig.ident)
```
```{r}
save(Seurat8, file = paste0(OUTPUT_PATH, "10_2021-42-set5", ".Robj"))
```
############################################## MAKE SURE BEST OBJECT IT IS #################################################
###########################################################################################################
############################################################################################
###########################################################################
#############################################################
##############################################
##############################
###############
######
###

## Mitochondrial percentage versus nFeatures
```{r mito_vs_nfeatures}
df<-data.frame(identity=Seurat8@misc$old_meta_data$souporcell_classif,percent.mito=Seurat8@misc$old_meta_data$percent.mito,nFeature_RNA=Seurat8@misc$old_meta_data$nFeature_RNA)

ggplotly(ggplot(df,aes(x=nFeature_RNA,y=percent.mito,color=identity))+geom_point())
```
## UMAP according to genes expression
### findAllMarkers
```{r, message=FALSE}
Idents(Seurat1) <- "RNA_snn_res.0.5"
if(! file.exists(paste0(OUTPUT_PATH, "FindAllMarkers_clusters_res0.5_results_",".Robj"))){
Seurat_markers <- FindAllMarkers(object = Seurat1, only.pos = FALSE, min.pct = 0.25, thresh.use = 0.25, do.print = TRUE)
  save(Seurat_markers, file = paste0(OUTPUT_PATH, "FindAllMarkers_clusters_res0.5_results_",".Robj"))
}else{
  load(paste0(OUTPUT_PATH, "FindAllMarkers_clusters_res0.5_results_",".Robj"))
}

datatable(Seurat_markers, options = list(pageLength = 100)) %>% formatRound(2, 1) %>% formatSignif(c(1,5))
```
The following plots show the expression of each cluster's top marker based on avg_logFC.
```{r umapClusterMarkers, fig.width = 5, fig.height = 7}
top_genes_feature_plot <- Seurat_markers %>% group_by(cluster) %>% top_n(4, avg_logFC)

FeaturePlot(object = temoins, features = top_genes_feature_plot$gene[1:4], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[5:8], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[9:12], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[13:16], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[12:20], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[21:24], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[25:28], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[29:32], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[33:36], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[37:40], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[41:44], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[45:48], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[49:52], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[53:56], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))

FeaturePlot(object = Seurat1, features = top_genes_feature_plot$gene[57:60], cols = c("grey", "light blue","cyan3","cyan4","dodgerblue3","blue","mediumslateblue","purple","orchid3","red","brown","black"))
```
### Hand picked
```{r umapMarkers1, fig.width = 7.6, fig.height = 10, message=FALSE}
Idents(Témoins_alone) <- "RNA_snn_res.0.5"
FeaturePlot(object = Témoins, features = "FLT3", reduction = "umap", order = TRUE, pt.size = 1 , ncol = 2, cols = c("grey86","red"))
```
## UMAP according to {.tabset}
### %mito
```{r percentmito,  fig.width = 5, fig.height = 7}
  Tsne<-data.frame(
    UMAP_1 = mutants@reductions$umap@cell.embeddings[,1],
    UMAP_2= mutants@reductions$umap@cell.embeddings[,2],
    gene= mutants@meta.data$percent.mito)

  HTO= mutants@meta.data$orig.ident
  Max=max(mutants@meta.data$percent.mito)
  Min=min(mutants@meta.data$percent.mito)

  ggplot(Tsne,aes(x=UMAP_1,y=UMAP_2))+geom_point(aes(color=gene,shape=HTO))+
    scale_colour_gradient2(low = "lightgrey",mid="grey",high="red",name="percent.mito",midpoint=(Max+Min)/2)
```
### nFeature
```{r nFeature,  fig.width = 5, fig.height = 7}
  Tsne<-data.frame(
    UMAP_1 = j6_patient@reductions$umap@cell.embeddings[,1],
    UMAP_2= j6_patient@reductions$umap@cell.embeddings[,2],
    gene= j6_patient@meta.data$nFeature_RNA)

  Days = j6_patient@meta.data$orig.ident
  Max=max(j6_patient@meta.data$nFeature_RNA)
  Min=min(j6_patient@meta.data$nFeature_RNA)

  ggplot(Tsne,aes(x=UMAP_1,y=UMAP_2))+geom_point(aes(color=gene, shape = Days)) + 
    scale_colour_gradient2(low = "blue",mid="orange",high="red",name="Genes expressed",midpoint=(Max+Min)/2)
```
### nCount
```{r nCount,  fig.width = 5, fig.height = 7}
  Tsne<-data.frame(
    UMAP_1 = j11_patient@reductions$umap@cell.embeddings[,1],
    UMAP_2 = j11_patient@reductions$umap@cell.embeddings[,2],
    gene = j11_patient@meta.data$nCount_RNA)

  Days = j11_patient@meta.data$orig.ident
  Max=max(j11_patient@meta.data$nCount_RNA)
  Min=min(j11_patient@meta.data$nCount_RNA)

  ggplot(Tsne,aes(x=UMAP_1,y=UMAP_2))+geom_point(aes(color=gene, shape = Days))+
    scale_colour_gradient2(low = "blue",mid="orange",high="red",name="mRNA count",midpoint=(Max+Min)/2)
```
### Cell cycle phases
```{r phases,  fig.width = 5, fig.height = 7}
# Assign Cell-Cycle Scores
Témoins_alone <- CellCycleScoring(object = Témoins_alone, s.features = cc.genes$s.genes, g2m.features = cc.genes$g2m.genes, set.ident = TRUE,)
# view cell cycle scores and phase assignments
# Plot phases
DimPlot(Témoins_alone, reduction = "umap", 
        group.by = "Phase", 
        #split.by = "hash.ID", 
        pt.size = 1,
        ncol = 2)
```
S score
```{r  Sscore, fig.width = 5, fig.height = 7}
# Plot S score
  Tsne<-data.frame(
    UMAP_1 = Seurat1@reductions$umap@cell.embeddings[,1],
    UMAP_2= Seurat1@reductions$umap@cell.embeddings[,2],
    gene= Seurat1@meta.data$S.Score
  )
  HTO= Seurat1@meta.data$hash.ID
  Max=max(Seurat1@meta.data$S.Score)
  Min=min(Seurat1@meta.data$S.Score)

  ggplot(Tsne,aes(x=UMAP_1,y=UMAP_2))+geom_point(aes(color=gene,shape=HTO))+
    scale_colour_gradient2(low = "blue",mid="orange",high="red",name="S score",midpoint=(Max+Min)/2)
```
G2M score
```{r G2Mscore,  fig.width = 5, fig.height = 7}
# Plot G2M scores
  Tsne<-data.frame(
    UMAP_1 = Seurat1@reductions$umap@cell.embeddings[,1],
    UMAP_2= Seurat1@reductions$umap@cell.embeddings[,2],
    gene= Seurat1@meta.data$G2M.Score)

  HTO= Seurat1@meta.data$hash.ID
  Max=max(Seurat1@meta.data$G2M.Score)
  Min=min(Seurat1@meta.data$G2M.Score)

 ggplot(Tsne,aes(x=UMAP_1,y=UMAP_2))+geom_point(aes(color=gene,shape=HTO))+
    scale_colour_gradient2(low = "blue",mid="orange",high="red",name="G2M score",midpoint=(Max+Min)/2)
```